---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SampleSizeR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/SampleSizeR)](https://CRAN.R-project.org/package=SampleSizeR)

<!-- badges: end -->

The package SampleSizeR for R statistical software provides an intuitive Shiny 
application to easily perform sample size estimation and power analysis for
interventional and observational clinical studies.
To this end, SampleSizeR facilitates the conversion of design-specific assumptions 
into the parameters required by generic sample size calculation procedures.
For designs that lack analytical solutions, a simulation engine is provided.


## Installation

You can install the development version of SampleSizeR like so:

``` r
remotes::install_github(repo = "waidschrat/SampleSizeR")
```

## Run Application Online

The application is available from (https://htaor.shinyapps.io/samplesizer/)

## Run Application Locally

The following examples illustrates how to run the application locally.

```{r example}
# library(SampleSizeR)
# 
# # Arguments
# init <- list(ee = 3.07, se = 1.19, delta = c(-3, 0, 3), alpha = 0.025)
# cols <- list(col_lower = "#F5FF82", col_upper = "#27CC1E")
# 
# # Pass Arguments to Locally Run Shiny Application using run_app()
# if(interactive()){
#   run_app(init = init, cols = cols)
# }
# 
# # Alternatively Generate and Customize Regions of Evidence Plot using ribbonROE()
# HM23.3 <- ribbonROE(ee = init$ee, se = init$se, delta = init$delta, alpha = init$alpha, 
#                     cols = c(cols$col_lower, cols$col_upper))$plot + 
#   ggplot2::annotate(geom = "point", y = init$ee, x = init$se, shape = 4) +
#   ggplot2::coord_flip(ylim = c(-5, 15))


```

