---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SampleSizeR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/SampleSizeR)](https://CRAN.R-project.org/package=SampleSizeR)

<!-- badges: end -->

The package SampleSizeR for R statistical software provides an intuitive Shiny 
application to easily perform sample size estimation and power analysis for
interventional and observational clinical studies.
To this end, SampleSizeR facilitates the conversion of design-specific assumptions 
into the parameters required by generic sample size calculation procedures.
For designs that lack analytical solutions, a simulation engine is provided.


## Installation

You can install the development version of SampleSizeR like so:

``` r
remotes::install_github(repo = "waidschrat/SampleSizeR")
```

## Run Application Online

The application is available from https://htaor.shinyapps.io/samplesizer

## Run Application Locally

The following example illustrates how to run the application locally.

```{r example}
library(SampleSizeR)

# Arguments for Power Analysis of Binary Outcome
init <- list("Risk_T"=0.2, #Event Risk in Treatment Arm
              "Risk_C"=0.1, #Event Risk in Comparator Arm
              "Sample"=c(32,512), # Total Sample Size
              "Prop_T"=0.7, # Proportion of Sample Allocated to Treatment Arm
              "Alpha"=0.025, # Type 1 Error Probability
              "Delta"=1) # Relevance Margin of Effect (Odds Ratio)

# Pass Arguments to Locally Run Shiny Application using run_app()
if(interactive()){
  run_app(init = init)
}

```

